Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-11 main.tex
wrote about the runtimes of the algorithms

    On the memory-constrained cluster, \heft could produce valid assignments in $14$ experiments out of $290$~($4.8\%$
    success rate).
    The successful schedules were achieved exclusively on the tiny workflows (with only two 200-task size-increased
    workflow among them).
    \heftbl could successfully schedule $38\%$ of workflows, \heftblc could schedule $49\%$, while \heftmm
    could still schedule all of the workflows, including even the largest ones.
    As also observed on the normal cluster, \heftmm seems to be less affested by the size of the workflow when scheduling
    it.
    The makespans it produces are larger, but it seems to order the vertices in a similar way on both the small and the large workflows,
    rather than resorting to more memory-consuming ordering that other heuristics and the baseline produces.
    This makes it especially valuable for very large workflows in situations of very constrained memory in the cluster.

@@

    \subsubsection{Runtimes of the algorithm}

>>>>

    On the memory-constrained cluster, \heft could produce valid assignments in $14$ experiments out of $290$~($4.8\%$
    success rate).
    The successful schedules were achieved exclusively on the tiny workflows (with only two 200-task size-increased
    workflow among them).
    \heftbl could successfully schedule $38\%$ of workflows, \heftblc could schedule $49\%$, while \heftmm
    could still schedule all of the workflows, including even the largest ones.
    As also observed on the normal cluster, \heftmm seems to be less affected by the size of the workflow when scheduling
    it.
    The makespans it produces are larger, but it seems to order the vertices in a similar way on both the small and the large workflows,
    rather than resorting to more memory-consuming ordering that other heuristics and the baseline produces.
    This makes it especially valuable for very large workflows in situations of very constrained memory in the cluster.

@@

    \subsubsection{Runtimes of the algorithm}
    To be able to answer the runtime system without holding it up for too long, the scheduler needs to provide a fast answer.
    Our bottom-level-based heuristics \heftbl and \heftblc provide smaller runtimes and also scale better with growing workflow
    sizes~(see Fig.~\ref{fig:runtimes-abs} and Fig.~\ref{fig:runtimes-abs}).
    Their runtimes are similar and grow from tens of miliseconds for the smallest workflows to $25-27$ seconds for the largest workflows.
    \heftmm, however, needs to compute a memory-optimal traversal of the entire workflow to compute the ranks of the tasks,
    so its runtime scales from also rens of miliseconds for the smalest workflows to thousands of seconds - $1172.7$ for \numprint{20000}-task workflows and
    $2994.9$ seconds for the largest, \numprint{30000}-task workflows.
    This increased runtime is, though, offset by the unique $100\%$ success rate this algorithm shows when scheduling large
    workflows in difficult (memory-constrained) setups.
